Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Review section on low density system

    \subsection{Low density system}
        It is safe to say that the effect of adding a Jastrow factor is significant,
        i.e. the increase in
            energy for the system as the interaction is switched on is much higher
            than the uncertainty of the energy. A simple look at \autoref{fig:interacting}
            will be proof enough as the error bars of the figure are not discernible.
        On the other hand, the energy added to the system by including interaction
        is not very high compared to the energy of the system as a whole. For the
        larger of the interacting systems we have looked at, with $n=100$ particles,
        The interaction add only a mere $9\%$ extra energy (see \autoref{tab:interacting_optimal}).
        Studying \autoref{fig:one_body_density_100} will reveal the same.

        The reason for this stems from the assumption which justifies that
        adding only two-body interaction is sufficient to model all interaction to a
        reasonable extent. This assumption is justified by the fact that alkali and
        atomic hydrogen systems\footnote{Systems similar to our toy model}
        are dilute. For gases of alkali atoms confined in magnetic or optical traps
        the average distance between atoms is much larger than the range of
        inter-atomic interaction. The probability is high that atoms very seldom
        interact and if so, just with one other atom.

>>>>

    \subsection{Low density system}
        It is safe to say that the effect of adding a Jastrow factor is
        significant, i.e. the increase in energy for the system as the
        interaction is switched on is much higher than the uncertainty of the
        energy. A simple look at \autoref{fig:interacting} will be proof enough
        as the error bars of the figure are not discernible.  On the other hand,
        the energy added to the system by including interaction is not very high
        compared to the energy of the system as a whole. For the larger of the
        interacting systems we have looked at, with $N=100$ particles, the
        interaction add only a mere $9\%$ extra energy compared to the
        non-interacting system (see \autoref{tab:interacting_optimal}).
        Studying \autoref{fig:one_body_density_100} will reveal the same trend
        in the distribution of the particles.

        The reason for this is two-fold.
        \begin{enumerate}
            \item The hard sphere radius is vanishingly small. By increasing the
                hard sphere radius the particles will contribute more
                significantly to the local energy. The particles will also be
                more spread out thus occupying a larger configuration space.

            \item The assumption which justifies that adding only two-body
                interaction is sufficient to model all interactions to a
                reasonable extent. This assumption is justified by the fact that
                alkali and atomic hydrogen systems\footnote{Systems similar to
                our toy model.} are dilute. For gases of alkali atoms confined
                in magnetic or optical traps the average distance between atoms
                is much larger than the range of inter-atomic interaction. The
                probability is high that atoms very seldom interact and if so,
                just with one other atom.
        \end{enumerate}
